A Decision Procedure for (Co)datatypes in SMT Solvers

### 2016-02-08 sister/sister.tex
submitted first version
more

%%% TODO: Put http://lara.epfl.ch/~reynolds/JAR-CADE2015-cdt/ online
%%% TODO: Mealy machine minimization
%%% TODO: Give small example where Single is needed

%%% GOOD IDEAS in impl of codata models:
%%% 1. de Bruijn
%%% 2. enum: "X nat"
%%% 3. norm by DFA minim
%%% 4. check membership in bad set by matching

\documentclass[smallcondensed,draft]{svjour3}

\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[scaled=.82]{beramono}
\usepackage[scaled=.86]{helvet}
\usepackage{booktabs}
\usepackage{bussproofs}
\usepackage{cite}
\usepackage{color}
\usepackage{mathptmx}
\usepackage{mathpartir}
\usepackage{stmaryrd}
\usepackage{subfigure}
\usepackage{textcomp}
\usepackage{url}
\usepackage[all]{xy}

@@

\spnewtheorem{examplex}{Example}{\itshape}{\rmfamily}

@@

\newcommand\xend{{\hfill$\scriptstyle\blacksquare$}}
\newcommand\xqed{{\hfill$\scriptstyle\squareforqed$}}

@@

\author {Andrew Reynolds \and Jasmin Christian Blanchette\thanks{In memoriam Morgan Deters 1979--2015}}
\authorrunning {A. Reynolds \and J. C. Blanchette}

\institute{
Andrew Reynolds
\at \'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland
\and
Jasmin Christian Blanchette%, funded by DFG grant \textit{Hardening the Hammer} (Ni\,491\slash 14-1)
\at Inria \& LORIA, Nancy, France \\
Max-Planck-Institut f\"ur Informatik, Saarbr\"ucken, Germany}

@@

@@

%% The institutions above shouldn't count as footnotes
\setcounter{footnote}{0}

@@

\bibliographystyle{spmpsci}
\bibliography{bib}{}

>>>>

\documentclass[letter]{article}
% The file ijcai16.sty is the style file for IJCAI-16 (same as ijcai07.sty).
\usepackage{ijcai16}

\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[scaled=.82]{beramono}
\usepackage[scaled=.86]{helvet}
\usepackage{booktabs}
\usepackage{bussproofs}
%\usepackage{cite}
\usepackage{color}
\usepackage{mathptmx}
\usepackage{mathpartir}
\usepackage{stmaryrd}
\usepackage{subfigure}
\usepackage{textcomp}
\usepackage{url}
\usepackage[all]{xy}

@@

\newtheorem{examplex}{Example}%{\itshape}{\rmfamily}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

@@

\newcommand\xend{{\hfill$\scriptstyle\blacksquare$}}
\newcommand\xqed{{\hfill$\scriptstyle\square$}}

@@

\author {Andrew Reynolds \and Jasmin Christian Blanchette\thanks{In memoriam Morgan Deters 1979--2015} \\
Department of Computer Science, The University of Iowa, USA \and \\
Inria Nancy -- Grand Est \& LORIA Villers-l\`es-Nancy, France
}

%\authorrunning {A. Reynolds \and J. C. Blanchette}

%\institute{
%Andrew Reynolds
%\at \'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland
%\and
%Jasmin Christian Blanchette%, funded by DFG grant \textit{Hardening the Hammer} (Ni\,491\slash 14-1)
%\at Inria \& LORIA, Nancy, France \\
%Max-Planck-Institut f\"ur Informatik, Saarbr\"ucken, Germany}

@@

\begin{abstract}
New abstract.
\end{abstract}

  * a general introduction to automatic theorem proving \\

  * relation to AI
   * among the earliest AI goals
   * yet somewhat disconnected from mainstream AI
     (with some exceptions, e.g. Urban ..., MaSh)

  * followed by an intro to SMT and what it's used for \\
  * followed to why theories are important (more efficient reasoning) \\
  * followed to why (co)datatypes are important

  * both for proving
   * not finitely axiomatizable
  * and for model finding
   * Nunchaku

xxx

\section{Evaluation} % on Isabelle Problems}
\label{sec:evaluation}

\newpage

X

\newpage

@@

@@

\bibliographystyle{named}
\bibliography{bib}{}
